A meta-analysis of mental rotation ability in the first years of life

### 2022-04-19 code/analysis.Rmd
Improve Bayesian model
- Add explicit prior predivtie checks
- Align sensitivity analysis with Williams et al. (2018)

# Run prior predictive simulation
res_prior <- brm(
  yi | se(sei) ~ 1 + (1 | article / group),
  data = dat_both_mixed,
  prior = prior_c,
  cores = 4,
  chains = 4,
  iter = 2000,
  sample_prior = TRUE,
  save_pars = save_pars(all = TRUE)
)
summary(res_brm)

# Sensitivity analysis
list(
  "ic_uninformative" = c(
    prior(uniform(-3, 3), class = "Intercept"),
    prior(exponential(1), class = "sd")
  ),
  "ic_informative" = c(
    prior(normal(0, 0.2), class = "Intercept"),
    prior(exponential(1), class = "sd")
  ),
  "sigma_uninformative" = c(
    prior(normal(0, 1), class = "Intercept"),
    prior(uniform(0, 5), class = "sd")
  ),
  "sigma_informative" = c(
    prior(normal(0, 1), class = "Intercept"),
    prior(exponential(0.1), class = "sd")
  )
) %>%
  map(function(priors) update(res_brm, prior = priors)) -> res_sens
```

>>>>

# Run prior predictive simulation
res_prior <- brm(
  yi | se(sei) ~ 1 + (1 | article / group),
  data = dat_both_mixed,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  iter = 2000,
  cores = 4,
  control = list(adapt_delta = 0.99)
)
summary(res_prior)
# plot(res_prior)

# Run Bayesian multilevel model
res_brm <- update(res_prior, sample_prior = FALSE)
summary(res_brm)
# plot(res_brm)

# Sensitivity analysis
list(
  "interept_uninformative" = c(
    set_prior("uniform(-3, 3)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "interept_informative" = c(
    set_prior("normal(0, 0.2)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "sd_uninformative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("uniform(0, 10)", class = "sd", ub = 10)
  ),
  "sd_informative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("student_t(10, 0, 0.2)", class = "sd")
  )
) %>%
  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
map(res_sens, summary)
```
